Dominance Regions for Rank Two Cluster Algebras

### 2022-08-06 Annals of Combinatorics/submission.tex
Edits to the arXiv version

  \vspace{-1.05em}
  \end{theorem}
  \begin{remark}
    Explicit calculations reveal that for certain pairs of notable bases (e.g. greedy and triangular) most of the coeffiecients $q_{\lambda,\mu}$ are zero.
    Understanding this phenomenon might be worth further study.
  \end{remark}

@@

  \begin{lemma}
    For $i,\ell\in\ZZ$ and $\varepsilon\in\{\pm\}$, we have
    \begin{equation}
      \label{eq:long Chebyshev recursion}
      u_{i+\ell}^\varepsilon=\begin{cases} u_{\ell+1}^\varepsilon u_i^{-\varepsilon}-u_\ell^{-\varepsilon} u_{i-1}^\varepsilon & \text{\upshape if $\ell$ is odd;}\\ u_{\ell+1}^{-\varepsilon} u_i^\varepsilon-u_\ell^\varepsilon u_{i-1}^{-\varepsilon} & \text{\upshape if $\ell$ is even.} \end{cases}
    \end{equation}
  \end{lemma}
  \begin{proof}
    We work by induction on $\ell$ for all $i$ simultaneously, the cases $\ell=0,1$ being tautological and reproducing the defining recursions, respectively.
    Using the claim for $\ell>0$ and then the defining recursion twice, $u_{i+\ell+1}^\varepsilon$ can be rewritten for $\ell$ odd as
    \[
      u_{\ell+1}^\varepsilon u_{i+1}^{-\varepsilon}-u_\ell^{-\varepsilon} u_i^\varepsilon
      =u_{\ell+1}^\varepsilon(u_2^{-\varepsilon}u_i^\varepsilon-u_{i-1}^{-\varepsilon}) -u_\ell^{-\varepsilon} u_i^\varepsilon 
      =(u_2^{-\varepsilon} u_{\ell+1}^\varepsilon-u_\ell^{-\varepsilon}) u_i^\varepsilon-u_{\ell+1}^\varepsilon u_{i-1}^{-\varepsilon}
      =u_{\ell+2}^{-\varepsilon} u_i^\varepsilon - u_{\ell+1}^\varepsilon u_{i-1}^{-\varepsilon}
    \]
    and for $\ell$ even as
    \[
      u_{\ell+1}^{-\varepsilon} u_{i+1}^\varepsilon-u_\ell^\varepsilon u_i^{-\varepsilon}
      =u_{\ell+1}^{-\varepsilon}(u_2^\varepsilon u_i^{-\varepsilon}-u_{i-1}^\varepsilon) -u_\ell^\varepsilon u_i^{-\varepsilon}
      =(u_2^\varepsilon u_{\ell+1}^{-\varepsilon}-u_\ell^\varepsilon) u_i^{-\varepsilon}-u_{\ell+1}^{-\varepsilon} u_{i-1}^\varepsilon
      =u_{\ell+2}^\varepsilon u_i^{-\varepsilon}-u_{\ell+1}^{-\varepsilon} u_{i-1}^\varepsilon.
    \]
    This gives the claimed recursion for $\ell+1$.
    These calculations can be reversed to show the result for $\ell<0$.
  \end{proof}

@@

    For any $i\ne1$, we have
    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}=\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)\cdot\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}}.\]
    It follows that
    \[\lim_{i\to\infty} \frac{u_i^-}{u_{i-1}^+} = \lim_{i\to\infty} \left( \frac{\sqrt{c}}{2\sqrt{b}}\cdot\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)\cdot\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}} \right) = \frac{\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}+\sqrt{bc-4}\big),\]
    which is equivalent to the desired expression.
    Similarly, for $i\ne0$ we have
    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}=\frac{\big(\sqrt{bc}-\sqrt{bc-4}\big)\cdot\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)},\]
    so that
    \[\lim_{i\to\infty} \frac{u_{i-1}^-}{u_i^+} = \lim_{i\to\infty} \left( \frac{2\sqrt{c}}{\sqrt{b}}\cdot\frac{\big(\sqrt{bc}-\sqrt{bc-4}\big)\cdot\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)} \right) = \frac{\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}-\sqrt{bc-4}\big),\]
    which is again equivalent to the desired expression.
    This proves the claim for $i\to\infty$, the cases $i\to-\infty$ follow from these using $u_{-i}^\varepsilon=-u_i^\varepsilon$.

    For the final claim, observe that $\frac{u_{i+1}^{-\varepsilon}}{u_i^\varepsilon}<\frac{u_i^{-\varepsilon}}{u_{i-1}^\varepsilon}$ and $\frac{u_{i-1}^{-\varepsilon}}{u_i^\varepsilon}<\frac{u_i^{-\varepsilon}}{u_{i+1}^\varepsilon}$ are both equivalent to $u_{i+1}^{-\varepsilon}u_{i-1}^\varepsilon<u_i^{-\varepsilon}u_i^\varepsilon$.
    This inequality is then immediate, for $i>0$, from the following inductions:
    \begin{align*}
      u_{i+1}^{-}u_{i-1}^+
      =(cu_i^+-u_{i-1}^{-})u_{i-1}^+
      =cu_i^+ u_{i-1}^+-u_{i-1}^{-} u_{i-1}^+
      <cu_i^+ u_{i-1}^+-u_i^+ u_{i-2}^{-}
      =u_i^+(cu_{i-1}^+-u_{i-2}^{-})
      =u_i^+ u_i^{-};
      \\
      u_{i+1}^{+}u_{i-1}^-
      =(bu_i^--u_{i-1}^{+})u_{i-1}^-
      =bu_i^- u_{i-1}^--u_{i-1}^{+} u_{i-1}^-
      <bu_i^- u_{i-1}^--u_i^- u_{i-2}^{+}
      =u_i^-(bu_{i-1}^--u_{i-2}^{+})
      =u_i^- u_i^{+}.
    \end{align*}
    Again the case $i<0$ then follows from $u_{-i}^\varepsilon=-u_i^\varepsilon$.
  \end{proof}

@@

  Write $\phi_0:\RR^2\to\RR^2$ for the identity map and define piecewise-linear maps $\phi_{\pm 1}:\RR^2\to\RR^2$ as follows:
  \begin{equation}
    \label{eq:forward mutation 1}
    \phi_1(\lambda)
    :=
    \begin{cases} 
      (-\lambda_0,c\lambda_0+\lambda_1) & \text{if $\lambda_0 \ge 0$;}\\
      (-\lambda_0,\lambda_1) & \text{if $\lambda_0 < 0$;}
    \end{cases}
    \qquad
    \phi_{-1}(\lambda)
    :=
    \begin{cases} 
      (\lambda_0,-\lambda_1) & \text{if $\lambda_1 \ge 0$;}\\
      (\lambda_0+b\lambda_1,-\lambda_1) & \text{if $\lambda_1 < 0$.}
    \end{cases}
  \end{equation}
  For $k\in\ZZ$ with $|k|>1$, define piecewise-linear maps
  \[\phi_k
    :=
    \begin{cases}
      (\phi_{-1}^{-1}\phi_1)^j & \text{if $k=2j$;}\\
      \phi_1(\phi_{-1}^{-1}\phi_1)^j & \text{if $k=2j+1$.}\\
    \end{cases}
  \]
  These determine the dominance region as we paraphrase from \cite[Section 3.1]{Qin19}.
  \begin{definition}
    \label{def:dominance}
    For $\lambda=(\lambda_0,\lambda_1)\in\ZZ^2$ and $k\in\ZZ$, define cones 
    \[\cC_k(\lambda)
      :=
      \begin{cases}
        \{(\lambda_0-r,\lambda_1+s):r,s\in\RR_{\ge0}\} & \text{if $k=2j$;}\\
        \{(\lambda_0+r,\lambda_1-s):r,s\in\RR_{\ge0}\} & \text{if $k=2j+1$.}
      \end{cases}
    \]
    The \emph{dominance region} $\cP_\lambda$ is the intersection  $\bigcap_{k\in\ZZ}\phi_k^{-1}\cC_k(\phi_k\lambda)$.
    When $\mu\in\cP_\lambda$, we say \emph{$\lambda$ dominates $\mu$}.
  \end{definition}

@@

  By an eigenvector of a piecewise-linear map $\phi$, we will mean a vector $\lambda$ such that there exists a positive scalar $\nu$ so that $\phi(\lambda)=\nu\lambda$.
  \begin{lemma}
    Any nonzero eigenvector of $\phi_2$ is a positive multiple of one of the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)\!$.
  \end{lemma}
  \begin{proof}
    First observe that, by equation \eqref{eq:forward two step mutation}, the equation $\phi_2(\lambda)=\nu\lambda$ cannot be satisfied with a positive $\nu$ unless $\lambda_0\ge 0$ and $c\lambda_0+\lambda_1\ge 0$.
    In this region, $\phi_2$ is linear with eigenvalue $\nu$ satisfying $\nu^2-(bc-2)\nu+1=0$, i.e.~$\nu=\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}$.
    We thus require 
    \[\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_0=(bc-1)\lambda_0+b\lambda_1 \qquad\text{and}\qquad \frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_1= -c\lambda_0-\lambda_1,\]
    or equivalently
    \[\frac{-bc\pm\sqrt{bc(bc-4)}}{2b}\lambda_0=\lambda_1 \qquad\text{and}\qquad \frac{-bc\mp\sqrt{bc(bc-4)}}{2c}\lambda_1=\lambda_0.\]
    As these represent the same relationship, the result immediately follows by inspection.
  \end{proof}

@@

  It will be useful to have explicit expressions for $\phi_k(\lambda)$ for $\lambda\in\cI$.
  \begin{lemma}
    \label{le:imaginary transformations}
    For $j\in\ZZ$ and $\lambda\in\cI$, we have
    \begin{align*}
      \phi_{2j}(\lambda)&=(u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,-u_{2j}^-\lambda_0-u_{2j-1}^+\lambda_1);\\
      \phi_{2j+1}(\lambda)&=(-u_{2j+1}^-\lambda_0-u_{2j}^+\lambda_1,u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1).
    \end{align*}
  \end{lemma}
  \begin{proof}
    We work by induction on $j$, the case $j=0$ being clear from the definitions.
    For $\lambda\in\cI$, the action of~$\phi_2$ from \eqref{eq:forward two step mutation} can be rewritten as
    \[\phi_2(\lambda)=(u_3^-\lambda_0+u_2^+\lambda_1,-u_2^-\lambda_0-u_1^+\lambda_1).\]
    Therefore, after applying the equivalences for odd Chebyshev polynomials from Remark~\ref{rem:equivalences}, we have
    \begin{align*}
      \phi_{2j+2}(\lambda)&=\phi_2\phi_{2j}(\lambda)\\
      &=\big( (u_3^- u_{2j+1}^+-u_2^+u_{2j}^-)\lambda_0+(u_3^-u_{2j}^+-u_2^+u_{2j-1}^-)\lambda_1,-(u_2^-u_{2j+1}^+-u_1^+u_{2j}^-)\lambda_0-(u_2^-u_{2j}^+-u_1^+u_{2j-1}^-)\lambda_1 \big)\\
      &=(u_{2j+3}^+\lambda_0+u_{2j+2}^+\lambda_1, -u_{2j+2}^-\lambda_0-u_{2j+1}^-\lambda_1),
    \end{align*}
    where the last equality uses \eqref{eq:long Chebyshev recursion} with $i=2j+1$ and $\ell=2$.
    Using Remark~\ref{rem:equivalences} again, this is equivalent to the desired expression.

@@

    Assuming the inequalities (a)-(d) hold for $i$, we apply Lemma~\ref{le:transformed inequalities} for $\phi_2^{-1}$.
    Both of the boundary rays corresponding to the inequalities (a) and (d) lie entirely in the region where $\phi_2^{-1}$ acts according to the matrix~$\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, also the boundary segment corresponding to (b) intersects this region.
    Thus applying Lemma~\ref{le:transformed inequalities} to (a) gives the inequality 
    \[u_{2i+2}^-\mu_0+u_{2i+1}^+\mu_1=(u_3^+u_{2i}^--u_2^-u_{2i-1}^+)\mu_0+(u_2^+u_{2i}^--u_1^-u_{2i-1}^+)\mu_1\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1,\]
    which is the inequality (a) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}; while applying this to (d) gives the inequality 
    \[-u_{2i+1}^-\mu_0-u_{2i}^+\mu_1=(-u_3^+u_{2i-1}^-+u_2^-u_{2i-2}^+)\mu_0+(-u_2^+u_{2i-1}^-+u_1^-u_{2i-2}^+)\mu_1\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
    which is the inequality (d) for $i+1$ again by Lemma~\ref{eq:long Chebyshev recursion}; finally applying this to (b) gives the inequality 
    \[u_{2i+3}^-\mu_0+u_{2i+2}^+\mu_1=(u_3^+u_{2i+1}^--u_2^-u_{2i}^+)\mu_0+(u_2^+u_{2i+1}^--u_1^-u_{2i}^+)\mu_1\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
    which is the inequality (b) for $i+1$.
    Similarly, the boundary segment corresponding to (c) lies entirely in the region where $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & -1 \end{array}\right]$.
    Thus applying Lemma~\ref{le:transformed inequalities} to (c) gives the inequality 
    \[-u_{2i+1}^-\mu_0-u_{2i}^+\mu_1=(u_1^+u_{2i-1}^--u_2^-u_{2i}^+)\mu_0+(-u_0^+u_{2i-1}^--u_1^-u_{2i}^+)\mu_1\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
    which is the inequality (d) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, in particular we see that the segment determined by (c) and the ray determined by (d) align in the image.
    Lastly, the boundary segment corresponding to (b) also intersects the regions where $\phi_2^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$ and $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$ respectively.
    Applying Lemma~\ref{le:transformed inequalities} to (b) with the first matrix gives the inequality 
    \[-u_{2i+1}^-\mu_0+u_{2i+2}^+\mu_1=(-u_1^+u_{2i+1}^-+u_0^-u_{2i}^+)\mu_0+(u_2^+u_{2i+1}^--u_1^-u_{2i,+})\mu_1\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
    which is the inequality (c) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying Lemma~\ref{le:transformed inequalities} to (b) with the second matrix gives the inequality 
    \[-u_{2i+1}^-\mu_0-u_{2i}^+\mu_1\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
    which again reproduces the inequality (d) and aligns with the previous segment and ray in the image.
    This completes the induction on $i$, proving the Claim and the result for $k$ even.

>>>>

  \vspace{-1.05em}
  \end{theorem}
  \begin{remark}
    Explicit calculations reveal that for certain pairs of notable bases (e.g. greedy and triangular) most of the coefficients $q_{\lambda,\mu}$ are zero.
    Understanding this phenomenon might be worth further study.
  \end{remark}

@@

  \begin{lemma}
    For $i,\ell\in\ZZ$ and $\varepsilon\in\{\pm\}$, we have
    \begin{equation}
      \label{eq:long Chebyshev recursion}
      u_{i+\ell}^\varepsilon=\begin{cases} u_{\ell+1}^\varepsilon u_i^{-\varepsilon}-u_\ell^{-\varepsilon} u_{i-1}^\varepsilon & \text{\upshape if $\ell$ is odd;}\\ u_{\ell+1}^{-\varepsilon} u_i^\varepsilon-u_\ell^\varepsilon u_{i-1}^{-\varepsilon} & \text{\upshape if $\ell$ is even.} \end{cases}
    \end{equation}
  \end{lemma}
  \begin{proof}
    We work by induction on $\ell$ for all $i$ simultaneously, the cases $\ell=0,1$ being tautological and reproducing the defining recursions, respectively.
    Using the claim for $\ell>0$ and then the defining recursion twice, $u_{i+\ell+1}^\varepsilon$ can be rewritten for $\ell$ odd as
    \begin{align*}
      u_{\ell+1}^\varepsilon u_{i+1}^{-\varepsilon}-u_\ell^{-\varepsilon} u_i^\varepsilon
      &=u_{\ell+1}^\varepsilon(u_2^{-\varepsilon}u_i^\varepsilon-u_{i-1}^{-\varepsilon}) -u_\ell^{-\varepsilon} u_i^\varepsilon\\
      &=(u_2^{-\varepsilon} u_{\ell+1}^\varepsilon-u_\ell^{-\varepsilon}) u_i^\varepsilon-u_{\ell+1}^\varepsilon u_{i-1}^{-\varepsilon}\\
      &=u_{\ell+2}^{-\varepsilon} u_i^\varepsilon - u_{\ell+1}^\varepsilon u_{i-1}^{-\varepsilon}
    \end{align*}
    and for $\ell$ even as
    \begin{align*}
      u_{\ell+1}^{-\varepsilon} u_{i+1}^\varepsilon-u_\ell^\varepsilon u_i^{-\varepsilon}
      &=u_{\ell+1}^{-\varepsilon}(u_2^\varepsilon u_i^{-\varepsilon}-u_{i-1}^\varepsilon) -u_\ell^\varepsilon u_i^{-\varepsilon}\\
      &=(u_2^\varepsilon u_{\ell+1}^{-\varepsilon}-u_\ell^\varepsilon) u_i^{-\varepsilon}-u_{\ell+1}^{-\varepsilon} u_{i-1}^\varepsilon\\
      &=u_{\ell+2}^\varepsilon u_i^{-\varepsilon}-u_{\ell+1}^{-\varepsilon} u_{i-1}^\varepsilon.
    \end{align*}
    This gives the claimed recursion for $\ell+1$.
    These calculations can be reversed to show the result for $\ell<0$.
  \end{proof}

@@

    For any $i\ne1$, we have
    \[\scalebox{0.95}{$\displaystyle\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}=\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)\cdot\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}}$.}\]
    It follows that
    \begin{align*}
      \lim_{i\to\infty} \frac{u_i^-}{u_{i-1}^+}
      &=\lim_{i\to\infty} \left( \frac{\sqrt{c}}{2\sqrt{b}}\cdot\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)\cdot\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}} \right)\\
      &=\frac{\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}+\sqrt{bc-4}\big),
    \end{align*}
    which is equivalent to the desired expression.
    Similarly, for $i\ne0$ we have
    \[\scalebox{0.925}{$\displaystyle\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}=\frac{\big(\sqrt{bc}-\sqrt{bc-4}\big)\cdot\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)}$,}\]
    so that
    \begin{align*}
      \lim_{i\to\infty} \frac{u_{i-1}^-}{u_i^+}
      &=\lim_{i\to\infty} \left( \frac{2\sqrt{c}}{\sqrt{b}}\cdot\frac{\big(\sqrt{bc}-\sqrt{bc-4}\big)\cdot\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)} \right)\\
      &=\frac{\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}-\sqrt{bc-4}\big),
    \end{align*}
    which is again equivalent to the desired expression.
    This proves the claim for $i\to\infty$, the cases $i\to-\infty$ follow from these using $u_{-i}^\varepsilon=-u_i^\varepsilon$.

    For the final claim, observe that $\frac{u_{i+1}^{-\varepsilon}}{u_i^\varepsilon}<\frac{u_i^{-\varepsilon}}{u_{i-1}^\varepsilon}$ and $\frac{u_{i-1}^{-\varepsilon}}{u_i^\varepsilon}<\frac{u_i^{-\varepsilon}}{u_{i+1}^\varepsilon}$ are both equivalent to $u_{i+1}^{-\varepsilon}u_{i-1}^\varepsilon<u_i^{-\varepsilon}u_i^\varepsilon$.
    This inequality is then immediate, for $i>0$, from the following inductions:
    \begin{align*}
      u_{i+1}^{-}u_{i-1}^+
      &=(cu_i^+-u_{i-1}^{-})u_{i-1}^+
      =cu_i^+ u_{i-1}^+-u_{i-1}^{-} u_{i-1}^+\\
      &<cu_i^+ u_{i-1}^+-u_i^+ u_{i-2}^{-}
      =u_i^+(cu_{i-1}^+-u_{i-2}^{-})
      =u_i^+ u_i^{-};
      \\
      u_{i+1}^{+}u_{i-1}^-
      &=(bu_i^--u_{i-1}^{+})u_{i-1}^-
      =bu_i^- u_{i-1}^--u_{i-1}^{+} u_{i-1}^-\\
      &<bu_i^- u_{i-1}^--u_i^- u_{i-2}^{+}
      =u_i^-(bu_{i-1}^--u_{i-2}^{+})
      =u_i^- u_i^{+}.
    \end{align*}
    Again the case $i<0$ then follows from $u_{-i}^\varepsilon=-u_i^\varepsilon$.
  \end{proof}

@@

  Write $\phi_0:\RR^2\to\RR^2$ for the identity map and define piecewise-linear maps $\phi_{\pm 1}:\RR^2\to\RR^2$ as follows:
  \begin{equation}
    \label{eq:forward mutation 1}
    \phi_1(\lambda)
    :=
    \begin{cases} 
      (-\lambda_0,c\lambda_0+\lambda_1) & \text{if $\lambda_0 \ge 0$;}\\
      (-\lambda_0,\lambda_1) & \text{if $\lambda_0 < 0$;}
    \end{cases}
  \end{equation}
  \[
    \phi_{-1}(\lambda)
    :=
    \begin{cases} 
      (\lambda_0,-\lambda_1) & \text{if $\lambda_1 \ge 0$;}\\
      (\lambda_0+b\lambda_1,-\lambda_1) & \text{if $\lambda_1 < 0$.}
    \end{cases}
  \]
  For $k\in\ZZ$ with $|k|>1$, define piecewise-linear maps
  \[\phi_k
    :=
    \begin{cases}
      (\phi_{-1}^{-1}\phi_1)^j & \text{if $k=2j$;}\\
      \phi_1(\phi_{-1}^{-1}\phi_1)^j & \text{if $k=2j+1$.}\\
    \end{cases}
  \]
  These determine the dominance region as we paraphrase from \cite[Section 3.1]{Qin19}.
  \begin{definition}
    \label{def:dominance}
    For $\lambda=(\lambda_0,\lambda_1)\in\ZZ^2$ and $k\in\ZZ$, define cones 
    \[\cC_k(\lambda)
      :=
      \begin{cases}
        \{(\lambda_0-r,\lambda_1+s):r,s\in\RR_{\ge0}\} & \text{if $k=2j$;}\\
        \{(\lambda_0+r,\lambda_1-s):r,s\in\RR_{\ge0}\} & \text{if $k=2j+1$.}
      \end{cases}
    \]
    The \emph{dominance region} $\cP_\lambda$ is the intersection  $\bigcap_{k\in\ZZ}\phi_k^{-1}\cC_k(\phi_k\lambda)$.
    When $\mu\in\cP_\lambda$, we say \emph{$\lambda$ dominates $\mu$}.
  \end{definition}

@@

  By an eigenvector of a piecewise-linear map $\phi$, we will mean a vector $\lambda$ such that there exists a positive scalar $\nu$ so that $\phi(\lambda)=\nu\lambda$.
  \begin{lemma}
    Any nonzero eigenvector of $\phi_2$ is a positive multiple of one of the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)\!$.
  \end{lemma}
  \begin{proof}
    First observe that, by equation \eqref{eq:forward two step mutation}, the equation $\phi_2(\lambda)=\nu\lambda$ cannot be satisfied with a positive $\nu$ unless $\lambda_0\ge 0$ and $c\lambda_0+\lambda_1\ge 0$.
    In this region, $\phi_2$ is linear with eigenvalue $\nu$ satisfying $\nu^2-(bc-2)\nu+1=0$, i.e.~$\nu=\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}$.
    We thus require 
    \[\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_0=(bc-1)\lambda_0+b\lambda_1\,\,\,\text{and}\,\,\,\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_1= -c\lambda_0-\lambda_1,\]
    or equivalently
    \[\frac{-bc\pm\sqrt{bc(bc-4)}}{2b}\lambda_0=\lambda_1 \qquad\text{and}\qquad \frac{-bc\mp\sqrt{bc(bc-4)}}{2c}\lambda_1=\lambda_0.\]
    As these represent the same relationship, the result immediately follows by inspection.
  \end{proof}

@@

  It will be useful to have explicit expressions for $\phi_k(\lambda)$ for $\lambda\in\cI$.
  \begin{lemma}
    \label{le:imaginary transformations}
    For $j\in\ZZ$ and $\lambda\in\cI$, we have
    \begin{align*}
      \phi_{2j}(\lambda)&=(u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,-u_{2j}^-\lambda_0-u_{2j-1}^+\lambda_1);\\
      \phi_{2j+1}(\lambda)&=(-u_{2j+1}^-\lambda_0-u_{2j}^+\lambda_1,u_{2j+2}^-\lambda_0+u_{2j+1}^+\lambda_1).
    \end{align*}
  \end{lemma}
  \begin{proof}
    We work by induction on $j$, the case $j=0$ being clear from the definitions.
    For $\lambda\in\cI$, the action of~$\phi_2$ from \eqref{eq:forward two step mutation} can be rewritten as
    \[\phi_2(\lambda)=(u_3^-\lambda_0+u_2^+\lambda_1,-u_2^-\lambda_0-u_1^+\lambda_1).\]
    Therefore, after applying the equivalences for odd Chebyshev polynomials from Remark~\ref{rem:equivalences}, we have
    \begin{align*}
      \phi_{2j+2}(\lambda)&=\phi_2\phi_{2j}(\lambda)\\
      &=\Big( (u_3^- u_{2j+1}^+-u_2^+u_{2j}^-)\lambda_0+(u_3^-u_{2j}^+-u_2^+u_{2j-1}^-)\lambda_1,\\
      &\qquad-(u_2^-u_{2j+1}^+-u_1^+u_{2j}^-)\lambda_0-(u_2^-u_{2j}^+-u_1^+u_{2j-1}^-)\lambda_1 \Big)\\
      &=(u_{2j+3}^+\lambda_0+u_{2j+2}^+\lambda_1, -u_{2j+2}^-\lambda_0-u_{2j+1}^-\lambda_1),
    \end{align*}
    where the last equality uses \eqref{eq:long Chebyshev recursion} with $i=2j+1$ and $\ell=2$.
    Using Remark~\ref{rem:equivalences} again, this is equivalent to the desired expression.

@@

    Assuming the inequalities (a)-(d) hold for $i$, we apply Lemma~\ref{le:transformed inequalities} for $\phi_2^{-1}$.
    Both of the boundary rays corresponding to the inequalities (a) and (d) lie entirely in the region where $\phi_2^{-1}$ acts according to the matrix~$\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, also the boundary segment corresponding to (b) intersects this region.
    Thus applying Lemma~\ref{le:transformed inequalities} to (a) gives the inequality 
    \[u_{2i+2}^-\mu_0+u_{2i+1}^+\mu_1=(u_3^+u_{2i}^--u_2^-u_{2i-1}^+)\mu_0+(u_2^+u_{2i}^--u_1^-u_{2i-1}^+)\mu_1\le u_{2j}^-\lambda_0+u_{2j-1}^+\lambda_1,\]
    which is the inequality (a) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}; while applying this to (d) gives the inequality 
    \begin{align*}
      -u_{2i+1}^-\mu_0-u_{2i}^+\mu_1
      &=(-u_3^+u_{2i-1}^-+u_2^-u_{2i-2}^+)\mu_0+(-u_2^+u_{2i-1}^-+u_1^-u_{2i-2}^+)\mu_1\\
      &\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,
    \end{align*}
    which is the inequality (d) for $i+1$ again by Lemma~\ref{eq:long Chebyshev recursion}; finally applying this to (b) gives the inequality 
    \[u_{2i+3}^-\mu_0+u_{2i+2}^+\mu_1=(u_3^+u_{2i+1}^--u_2^-u_{2i}^+)\mu_0+(u_2^+u_{2i+1}^--u_1^-u_{2i}^+)\mu_1\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
    which is the inequality (b) for $i+1$.
    Similarly, the boundary segment corresponding to (c) lies entirely in the region where $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & -1 \end{array}\right]$.
    Thus applying Lemma~\ref{le:transformed inequalities} to (c) gives the inequality 
    \[-u_{2i+1}^-\mu_0-u_{2i}^+\mu_1=(u_1^+u_{2i-1}^--u_2^-u_{2i}^+)\mu_0+(-u_0^+u_{2i-1}^--u_1^-u_{2i}^+)\mu_1\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
    which is the inequality (d) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, in particular we see that the segment determined by (c) and the ray determined by (d) align in the image.
    Lastly, the boundary segment corresponding to (b) also intersects the regions where $\phi_2^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$ and $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$ respectively.
    Applying Lemma~\ref{le:transformed inequalities} to (b) with the first matrix gives the inequality 
    \begin{align*}
      -u_{2i+1}^-\mu_0+u_{2i+2}^+\mu_1
      &=(-u_1^+u_{2i+1}^-+u_0^-u_{2i}^+)\mu_0+(u_2^+u_{2i+1}^--u_1^-u_{2i,+})\mu_1\\
      &\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,
    \end{align*}
    which is the inequality (c) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying Lemma~\ref{le:transformed inequalities} to (b) with the second matrix gives the inequality 
    \[-u_{2i+1}^-\mu_0-u_{2i}^+\mu_1\le u_{2j+1}^-\lambda_0+u_{2j}^+\lambda_1,\]
    which again reproduces the inequality (d) and aligns with the previous segment and ray in the image.
    This completes the induction on $i$, proving the Claim and the result for $k$ even.
